DRAFT: v9.dev \\ Vibration Characterisation of Strollers and\\ Cargo Bicycles for Transporting Infants\\ \vspace{2mm} \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\

### 2025-11-20 main.tex
Update tex file with overleaf.

\title{
  DRAFT: v8 \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
}

@@

This paper provides measurements of vibration exerted on infant dummies in
strollers and cargo bicycles, which may be used as risk indicators for
discomfort or health effects. We equipped five strollers and two cargo bicycles
with inertial measurement units (IMU) and carried out 67 experiments on
different road surfaces and with different travel speeds, using dummies
representing 0, 3, and 9-month-old infants. We derived results using ISO~2631-1
frequency weightings and procedures to enable comparison with previous studies.
However, given that ISO~2631-1 is neither validated for children nor for lying
postures, we also report unweighted results to assess power spectrum and
bandwidth. We investigated the influence of vehicle, seat, body size, speed, and
road surface and provided recommendations to users, designers, and for future
research. Furthermore, as an example of how such measurements could be used for
assessing discomfort and health effects, we discuss these in the light of
thresholds suggested by ISO~2631-1 and Gao~et.~al~\cite{Gao2018}.

@@

\section*{Acknowledgement}
%
Neil Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, and Aernout
Dijkstra-Hellinga all provided important feedback on the preprint that helped
improve the paper. This work was financially supported by VeiligheidNL under the
``Project Trillingen bakfiets en wandelwagen'' and we thank VeiligheidNL
employee Mieke Cotterink for advice, support, and review of our work.

@@

%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-keiler-maxicosi-0-SeatBotacc_ver-rep0.png}
  \caption{Raw seat pan vertical acceleration versus time from session 015:
  Keiler tricycle during the shock test. ALT TEXT: Vertical acceleration versus
  time during an example shock test.}
  \label{fig:shock_time-history}
\end{figure}

>>>>

\title{
  DRAFT: v9.dev \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Including Recommendations for Users, Designers, Manufacturers, and Researchers} \\
}

@@

This paper provides measurements of vibration exerted on infant dummies in
strollers and cargo bicycles, which may be used as risk indicators for
discomfort or health effects. We equipped five strollers and two cargo bicycles
with inertial measurement units (IMU) and carried out 67 experiments on
different road surfaces and with different travel speeds, using dummies
representing 0, 3, and 9-month-old infants. We derived results using ISO~2631-1
frequency weightings and procedures to enable comparison with previous studies.
However, given that ISO~2631-1 is neither validated for children nor for lying
postures, we also report unweighted results to assess power spectrum and
bandwidth. We investigated the influence of vehicle, seat, body size, speed, and
road surface and provided recommendations for users, designers, and researchers.
Furthermore, as an example of how such measurements could be used for assessing
discomfort and health effects, we discuss these in the light of thresholds
suggested by ISO~2631-1 and Gao~et.~al~\cite{Gao2018}.

@@

\section*{Acknowledgement}
%
Neil Mansfield, Jim Papadopoulos, Malte Rothhämel, Stefan Schwanitz, Darek
Wieckowksi, and Aernout Dijkstra-Hellinga all provided important feedback on the
preprint that helped improve the paper. This work was financially supported by
VeiligheidNL under the ``Project Trillingen bakfiets en wandelwagen'' and we
thank VeiligheidNL employee Mieke Cotterink for advice, support, and review of
our work.

@@

%
\begin{figure}
  \centering
  \includegraphics[width=160mm]{fig/session015-t5-shock-bicycle-keiler-pebble-0-SeatBotacc_ver-rep0.png}
  \caption{Raw seat pan vertical acceleration versus time from session 015:
  Keiler tricycle during the shock test. ALT TEXT: Vertical acceleration versus
  time during an example shock test.}
  \label{fig:shock_time-history}
\end{figure}
